---
title: "BLiMP Human Experiment"
output: html_notebook
---

This is the R notebook for examining the human experiment set up of the BLiMP experiment.

```{r}
library(tidyverse)
library(ggplot2)
```
Load in `stims.csv` file
```{r}
stims <- read_csv("stims.csv")

```
We want to check the following things:
1. there are 67 distinct Groups
```{r}
n_distinct(stims$Group)
```

```{r}
stims %>%
  count(Group)
```

2. For each group, there are 100 target items and 10 filler items
```{r}
unique((stims %>%
  filter(trial_type == "target") %>%
  group_by(Group) %>%
  summarize(n_target = n()))$n_target)

unique((stims %>%
  filter(trial_type == "filler") %>%
  group_by(Group) %>%
  summarize(n_filler = n()))$n_filler)
```
3. For each group, there are 10 per configuration

```{r}
unique((stims %>%
  filter(trial_type == "target") %>%
  group_by(Group, config) %>%
  summarize(n_per_cond = n()))$n_per_cond)
```

4. across all groups, the number of trials per config or (config, trial) is the same
67 participaants * 100 trials = 6700 trials in total
6700 / 67 configurations = 100 trials per configuration
```{r}
unique((stims %>%
  filter(trial_type == "target") %>%
  group_by(config, pair_id) %>%
  summarize(ntrials_per_trial = n()))$ntrials_per_trial) # should be 10

unique((stims %>%
  filter(trial_type == "target") %>%
  group_by(config) %>%
  summarize(ntrials_per_config = n()))$ntrials_per_config) # should be 100
```

```{r}
stims %>%
  filter(trial_type == "target") %>%
  group_by(Group) %>%
  summarise(n_configs = n_distinct(config))

stims %>%
  filter(trial_type == "target") %>%
  distinct(Group, config) %>%
  count(config)
```


5. check all fillers
```{r}
fillers <- stims %>%
  filter(trial_type == "filler")
```

6. check that neighboring trials do not have the same configurations:

Right now none of the rows have this violation! Check!
```{r}
stims %>%
  group_by(Group) %>%
  filter(config == lag(config))
```


```{r}
# Set working directory to source file location

# User-defined function to read in PCIbex Farm results files
read.pcibex <- function(filepath, auto.colnames=TRUE, fun.col=function(col,cols){cols[cols==col]<-paste(col,"Ibex",sep=".");return(cols)}) {
  n.cols <- max(count.fields(filepath,sep=",",quote=NULL),na.rm=TRUE)
  if (auto.colnames){
    cols <- c()
    con <- file(filepath, "r")
    while ( TRUE ) {
      line <- readLines(con, n = 1, warn=FALSE)
      if ( length(line) == 0) {
        break
      }
      m <- regmatches(line,regexec("^# (\\d+)\\. (.+)\\.$",line))[[1]]
      if (length(m) == 3) {
        index <- as.numeric(m[2])
        value <- m[3]
        if (is.function(fun.col)){
         cols <- fun.col(value,cols)
        }
        cols[index] <- value
        if (index == n.cols){
          break
        }
      }
    }
    close(con)
    return(read.csv(filepath, comment.char="#", header=FALSE, col.names=cols))
  }
  else{
    return(read.csv(filepath, comment.char="#", header=FALSE, col.names=seq(1:n.cols)))
  }
}

# Read in results file
interim <- read.pcibex("interim.csv") %>%
  filter(Parameter=="Selection",
         trial_type=="target")
```

